%-------------------------
% Resume in LaTeX - Siddhanth Dwivedi
% Compile with pdflatex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

% ---------- PAGE STYLE ----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ---------- MARGINS ----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---------- SECTION FORMATTING ----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ---------- CUSTOM COMMANDS ----------
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{2pt}
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{\small\textbf{#1}} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ==================== DOCUMENT START ====================
\begin{document}

% ---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Siddhanth Dwivedi} \\ \vspace{1pt}
    \small
    \faPhone\ +91 8968562055 $|$
    \href{mailto:iamsiddhanthdwivedi@gmail.com}{\faEnvelope\ iamsiddhanthdwivedi@gmail.com} $|$
    \href{https://github.com/mafiaguy}{\faGithub\ mafiaguy} $|$
    \href{https://linkedin.com/in/mafiaguy}{\faLinkedin\ mafiaguy}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
\small{Infrastructure \& Reliability Engineer with 6+ years of experience operating and securing production cloud platforms on AWS. Core strengths in designing resilient architectures, building data pipelines (CDC/ETL), automating disaster recovery, and driving observability across distributed systems. Delivered 30\% AWS cost reduction, sub-hour disaster recovery RTOs, zero-downtime database failovers, and 99.92\% platform uptime. Experienced across ECS/Fargate container orchestration, auto-scaling, capacity planning, database operations, IaC (CDK), and incident response. Two-time Extra Mile Award recipient for operational excellence.}

% ---------- SKILLS ----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Reliability \& Operations:}{ Capacity Planning, Auto-Scaling (ECS, Redis/Valkey, OpenSearch), Disaster Recovery (IaC-based), Database Failover Testing, Incident Response \& RCA, Runbook Automation, On-Call Operations, SLI/SLO Monitoring} \\
        \textbf{Containers \& Orchestration:}{ Docker, Amazon ECS (EC2 \& Fargate), ECR, Kubernetes (personal projects), SOCI (Seekable OCI), Container Image Hardening, Task Definition Tuning, ARM/Graviton Migration} \\
        \textbf{Observability:}{ CloudWatch Metrics, Logs, Alarms \& Dashboards, Log Insights, Anomaly Detection, X-Ray Distributed Tracing, Prometheus \& Grafana (personal projects), CloudTrail Audit Logging} \\
        \textbf{Data \& Pipelines:}{ PostgreSQL CDC (Debezium), Amazon MSK (Kafka), AWS Glue, Amazon Redshift, S3 Data Lake, Schema Mapping \& Retry Mechanisms} \\
        \textbf{Cloud \& Infrastructure:}{ AWS (EC2, Lambda, ALB/NLB, Route 53, S3, RDS, IAM, VPC, OpenSearch, MSK, Glue, Redshift, CloudFront, Security Hub, GuardDuty), IaC (AWS CDK, CloudFormation), Multi-AZ \& Multi-Region} \\
        \textbf{Security \& Compliance:}{ CIS Benchmarks, WAF, Shield, ISO 27001, GDPR, DPDPA, OWASP Top 10, CSPM, SAST (Snyk), AWS Inspector, Penetration Testing} \\
        \textbf{Languages \& Databases:}{ TypeScript, Python, Ruby, Node.js, PostgreSQL, MySQL, Valkey/Redis, OpenSearch}
    }}
\end{itemize}

% ---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart

    % ===== LEAD ROLE =====
    \resumeSubheading
      {Lead Infrastructure \& Security Operations Engineer}{May 2025 -- Present}
      {Great Learning}{Bangalore, India}

    \resumeSubheadingContinue{Reliability \& Disaster Recovery}{}
    \resumeItemListStart
        \resumeItem{Led production database failover drill with zero downtime --- PostgreSQL auto-reconnect monkey patch worked flawlessly, with only 2 minutes of degraded performance across all services.}
        \resumeItem{Moved OpenSearch, Redshift, and CloudFront to CDK-based IaC, closing the last critical gaps in disaster recovery --- infrastructure is now fully recreatable programmatically in under 2 hours.}
        \resumeItem{Automated OpenSearch snapshots and backups to S3, reducing disaster recovery RTO from \textasciitilde1 week to 30--40 minutes.}
        \resumeItem{Conducted comprehensive Multi-AZ audit across all AWS services, identified gaps, and created a remediation plan to improve fault tolerance and availability posture.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Scaling \& Performance}{}
    \resumeItemListStart
        \resumeItem{Implemented OpenSearch storage auto-scaling via Lambda and CloudWatch; cluster has scaled 10x in production over 4 months, maintaining 100\% availability.}
        \resumeItem{Migrated Redis to Valkey across all three production services (LTI, LMS, Website), achieving \textasciitilde20\% cost savings and lower P99 latencies via multithreading --- then successfully enabled auto-scaling on the clusters.}
        \resumeItem{Implemented dynamic scaling for background delayed jobs, significantly improving processing throughput and enabling elastic handling of variable workloads without manual intervention.}
        \resumeItem{Implemented ETag caching in CloudFront, reducing OPTIONS request latency from 300--400ms to 60--90ms by eliminating unnecessary round-trips to origin servers.}
        \resumeItem{Converted remaining EC2-based delayed job instances (LMS, LTI, Payments) to ECS Fargate, completing the move to fully serverless container operations.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Data Pipeline Engineering}{}
    \resumeItemListStart
        \resumeItem{Designed and deployed GL-CloudETL, an in-house ETL pipeline replacing a third-party tool, using Debezium $\rightarrow$ MSK  $\rightarrow$ Glue with schema mapping and retry mechanisms --- eliminating vendor dependency and reducing data pipeline costs.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Platform Engineering \& Developer Productivity}{}
    \resumeItemListStart
        \resumeItem{Built an AWS Cloud Manager application with Google SSO, enabling one-click ECS deployments, compute instance control, and ALB configuration --- used regularly to deploy/restart services without Jenkins dependency.}
        \resumeItem{Set up reproducible local development environments, reducing new developer onboarding from 3--4 days to 20--30 minutes. Deployed Android build pipeline on Mac Studio, cutting build time from 30 min to 7 min.}
        \resumeItem{Upgraded Ruby on Rails to 7.2.3 across four production services and upgraded all databases (MySQL 8.0.41, PostgreSQL 14.17) before end-of-support deadlines with zero unplanned downtime.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Security \& Compliance}{}
    \resumeItemListStart
        \resumeItem{Reduced Node.js Docker image vulnerabilities by 25 CVEs (including 6 High, 1 Critical) through base image upgrades (Node 19 $\rightarrow$ 22 LTS, Alpine 3.17 $\rightarrow$ 3.22).}
        \resumeItem{Adopted AWS Inspector for shift-left code security scanning across all applications; conducted security risk assessment of 27 AI tools to establish organizational guardrails.}
        \resumeItem{Supported ISO 27001, GDPR, and DPDPA audits; closed all external VAPT findings within stipulated timelines.}
        \resumeItem{\textbf{Achievement:} Extra Mile Award (May 2025) for cost optimization and security leadership.}
    \resumeItemListEnd

    % ===== SENIOR ROLE =====
    \resumeSubheading
      {Senior Security Operations Engineer}{Apr 2022 -- May 2025}
      {Great Learning}{Bangalore, India}

    \resumeSubheadingContinue{Reliability \& Incident Response}{}
    \resumeItemListStart
        \resumeItem{Contributed to achieving 99.92\% platform uptime across all production services. Owned on-call incident response, RCA authoring, and runbook creation for production infrastructure.}
        \resumeItem{Deployed CDK-based disaster recovery systems and conducted production/staging DR drills, achieving full infrastructure recreation in under 2 hours with minimal data loss.}
        \resumeItem{Implemented zero-downtime database reconnection strategy during RDS auto-upgrades, eliminating 20--30 minutes of previously required redeployment downtime.}
        \resumeItem{Resolved a 4-year-old HLS video playback failure on iOS browsers by architecting a dedicated service handling 800 RPS, replacing a costly Lambda@Edge approach.}
        \resumeItem{Orchestrated DDoS resilience testing in staging and production, validating autoscaling to handle 5x traffic spikes and fine-tuning scaling policies across multiple iterations.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Scaling \& Cost Optimization}{}
    \resumeItemListStart
        \resumeItem{Cut AWS infrastructure spend by 30\% through ARM/Graviton migration across ECS, RDS, Redis, and OpenSearch, combined with target-tracking autoscaling and resource right-sizing.}
        \resumeItem{Implemented SOCI (Seekable OCI) for all containerized applications, reducing container startup time by 70\% and enabling significantly faster autoscaling response.}
        \resumeItem{Scaled delayed job processing by splitting database tables (Website, Sales, Ad-Hoc), reducing Website RDS CPU by 20\% and enabling 50\% more background worker scale-out without additional DB cost.}
        \resumeItem{Reduced ECS build and deployment times from 30+ minutes to under 10 minutes, directly improving deployment velocity and rollback speed.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Observability \& Monitoring}{}
    \resumeItemListStart
        \resumeItem{Built and maintained CloudWatch observability stack --- custom metrics, dashboards, composite alarms, anomaly detection, and Log Insights queries --- providing end-to-end visibility into ECS service health, latency, and error rates.}
        \resumeItem{Created infrastructure-wide health alarms across CPU, memory, disk, and network for all services, enabling early detection and reducing mean time to resolution.}
        \resumeItem{Moved Jenkins deployment logs to CloudWatch for centralized log management, improving cross-service debugging and audit trail visibility.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Platform \& IaC}{}
    \resumeItemListStart
        \resumeItem{Migrated entire production infrastructure to IaC (AWS CDK/CloudFormation) --- VPC, IAM, RDS, Redis, ECS, WAF, S3, ALB, SQS, Transcoder --- enabling repeatable, drift-free, auditable deployments.}
        \resumeItem{Upgraded Ruby on Rails from 5.2 to 7.1 and Ruby from 2.5 to 3.3, reducing latency by 20--22\% and improving scalability by 30\%.}
        \resumeItem{Implemented AWS SSO with Google OAuth and automated IAM key rotation via Lambda, reducing manual toil and improving access management.}
    \resumeItemListEnd

    \resumeSubheadingContinue{Security}{}
    \resumeItemListStart
        \resumeItem{Raised AWS Foundational Security Best Practices score from 64\% to 98\% and maintained CIS Benchmark v1.4 at 100\%. Achieved ISO 27001:2013 certification.}
        \resumeItem{Hardened Docker images with multi-stage builds, non-root users, and minimal base images --- reducing critical/high vulnerabilities from hundreds to single digits per service.}
        \resumeItem{Integrated Snyk into CI/CD pipelines and conducted regular penetration testing across web and mobile applications.}
        \resumeItem{\textbf{Achievement:} Extra Mile Award (Sep 2023) for ISO certification success and advancing DevSecOps adoption.}
    \resumeItemListEnd

    % ===== JUNIOR ROLE =====
    \resumeSubheading
      {Security Operations Engineer}{Feb 2021 -- May 2022}
      {Great Learning}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Conducted penetration testing, source code reviews, and vulnerability assessments across web and mobile applications (iOS \& Android, OWASP Top 10).}
        \resumeItem{Managed WAF rules and CloudWatch alarm configurations, improving incident detection and response capabilities.}
        \resumeItem{Orchestrated phishing simulations and security awareness training, reducing employee risk behavior by 35\%.}
        \resumeItem{Built standardized security and operational reporting dashboards for leadership visibility into risk posture and system health.}
    \resumeItemListEnd

    % ===== INSTRUCTOR ROLE =====
    \resumeSubheading
      {Cyber Security Instructor}{Sep 2019 -- Feb 2021}
      {Great Learning}{Delhi, India}
    \resumeItemListStart
        \resumeItem{Delivered penetration testing and cloud security training sessions; mentored students on hands-on security practices.}
        \resumeItem{Developed and maintained cybersecurity curriculum content and lab environments.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% ---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Kubernetes Observability Home Lab} $|$ \emph{\href{https://github.com/mafiaguy}{github.com/mafiaguy}}}{}
    \resumeItemListStart
        \resumeItem{Deployed a multi-service application on a local Kubernetes cluster (Minikube/kind), configured Prometheus for metrics collection and alerting rules, and built Grafana dashboards for monitoring pod health, resource utilization, and service latency. Hands-on with Helm charts, kubectl, and Kubernetes networking.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {B.Tech, Computer Science \& Engineering}{2017 -- 2020}
      {Maharaja Surajmal Institute of Technology}{Delhi}
    \resumeSubheading
      {Diploma, Computer Science \& Engineering}{2013 -- 2016}
      {Government Polytechnic College}{Mohali}
\resumeSubHeadingListEnd

% ---------- ACHIEVEMENTS ----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Extra Mile Award} --- Great Learning (Sep 2023, May 2025) for exceptional contributions to ISO certification, DevSecOps adoption, and cloud cost/reliability optimization.
    }}
\end{itemize}

\end{document}
